### 2012-02-13 Text/paper.tex
First import.

\documentclass{article}
\title{Binary fluid simulations with complicated geometries}
\begin{document}
\maketitle
We will start description here.
\end{document}

### 2012-02-13 Symmetric/binary.cpp
Started writing a code for P&G.

@@ -1,0 +1,518 @@
+//Simple mass transfer
+
+
+#include <iostream>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdio.h>
+#include <stdlib.h>
+#include <cmath>
+#include <vector>
+
+//Domain size
+int NY;
+int NX;
+int NUM;
+
+//Other constants
+const int NPOP=9;
+const int radius=20;
+const int radius_droplet=10;
+
+//Time steps
+int N=100000;
+int NOUTPUT=1000;
+
+//Fields and populations
+double *f;
+double *f2;
+double *g;
+double *g2;
+double *phi;
+double *rho;
+double *ux;
+double *uy;
+int * geometry;
+
+std::vector<int> bb_nodes;
+std::vector<char>* dirs;
+std::vector<char> main_dir;
+
+//BGK relaxation parameter
+double omega=1.0/2.5;
+
+//Underlying lattice parameters
+double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
+int cx[]={0,1,0,-1,0,1,-1,-1,1};
+int cy[]={0,0,1,0,-1,1,1,-1,-1};
+int compliment[]={0,3,4,1,2,7,8,5,6};
+int symmetricx[NPOP];
+int symmetricy[NPOP];
+int symmetricxy_left[NPOP];
+int symmetricxy_right[NPOP];
+
+void writephase(std::string const & fname)
+{
+
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iY=0; iY<NY; iY++)
+	{
+		for (int iX=0; iX<NX; ++iX)	
+		{
+			int counter=iY*NX+iX;
+			fout<<phi[counter]<<" ";
+		}
+		fout<<"\n";
+	}
+}
+
+void writegeometry(std::string const & fname)
+{
+	std::string filename=fname+".dat";
+	std::ofstream fout(filename.c_str());
+	fout.precision(10);
+
+	for (int iY=0; iY<NY; iY++)
+	{
+		for (int iX=0; iX<NX; ++iX)	
+		{
+			int counter=iY*NX+iX;
+			fout<<geometry[counter]<<" ";
+		}
+		fout<<"\n";
[…]

### 2012-02-14 Symmetric/binary.cpp
Doing a program.

@@ -19,10 +19,11 @@ int NUM;
 const int NPOP=9;
 const int radius=20;
 const int radius_droplet=10;
+const double wall_gradient=0.0;
 
 //Time steps
-int N=100000;
-int NOUTPUT=1000;
+int N=100;
+int NOUTPUT=10;
 
 //Fields and populations
 double *f;
@@ -197,12 +198,14 @@ void collide_bulk()
     for(int counter=0;counter<NUM;counter++)
     {
 		double dense_temp=0.0;
+        double phase_temp=0.0;
 		double ux_temp=0.0;
 		double uy_temp=0.0;
 		
 		for(int k=0;k<NPOP;k++)
 		{
 			dense_temp+=f[counter*NPOP+k];
+            phase_temp+=g[counter*NPOP+k];
 			ux_temp+=f[counter*NPOP+k]*cx[k];
 			uy_temp+=f[counter*NPOP+k]*cy[k];
 		}
@@ -213,17 +216,27 @@ void collide_bulk()
 		rho[counter]=dense_temp;
 		ux[counter]=ux_temp;
 		uy[counter]=uy_temp;
+        phi[counter]=phase_temp;
         
-		double feqeq[NPOP];
+		double feqeq[NPOP],geqeq[NPOP];
 
 		for (int k=0; k<NPOP; k++)
+		{
 			feqeq[k]=weights[k]*(dense_temp+3.0*dense_temp*(cx[k]*ux_temp+cy[k]*uy_temp)
             						         +4.5*dense_temp*((cx[k]*cx[k]-1.0/3.0)*ux_temp*ux_temp
 															+(cy[k]*cy[k]-1.0/3.0)*uy_temp*uy_temp
 					    			                         +2.0*ux_temp*uy_temp*cx[k]*cy[k]));
-
+            geqeq[k]=weights[k]*(phase_temp+3.0*phase_temp*(cx[k]*ux_temp+cy[k]*uy_temp)
+                                            +4.5*phase_temp*((cx[k]*cx[k]-1.0/3.0)*ux_temp*ux_temp
+                                            +(cy[k]*cy[k]-1.0/3.0)*uy_temp*uy_temp
+                                            +2.0*ux_temp*uy_temp*cx[k]*cy[k]));
+            
+        }
 		for(int k=0; k < NPOP; k++)
+		{
[…]

### 2012-02-14 Symmetric/binary.cpp
First version of the code. Need a larger surface and a lot of different showcases to analyze.

@@ -10,20 +10,43 @@
 #include <cmath>
 #include <vector>
 
+//Uncomment if you want to clamp tau parameters
+//#define CLAMP_TAU
+
 //Domain size
 int NY;
 int NX;
 int NUM;
 
+//Time steps
+int N=10000;
+int NOUTPUT=100;
+int NSIGNAL=100;
+
 //Other constants
 const int NPOP=9;
 const int radius=20;
-const int radius_droplet=10;
-const double wall_gradient=0.0;
+const int radius_droplet=20;
+const double wall_gradient=-0.5;
 
-//Time steps
-int N=100;
-int NOUTPUT=10;
+const double phi_wall=1.5;
+const double rho_wall=0.5;
+const double force_x=0.0;
+const double force_y=0.0;
+
+//BGK relaxation parameter
+double omega_rho=1.0;
+double omega_phi=1.0;
+
+//Binary-liquid parameters
+double aconst=0.04;
+double kconst=0.04;
+double gammaconst=1.0;
+double tau_gas=1.0;
+double tau_liq=1.0;
+
+
+
 
 //Fields and populations
 double *f;
@@ -40,14 +63,24 @@ std::vector<int> bb_nodes;
 std::vector<char>* dirs;
 std::vector<char> main_dir;
 
-//BGK relaxation parameter
-double omega=1.0/2.5;
-
 //Underlying lattice parameters
 double weights[]={4.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/9.0,1.0/36.0,1.0/36.0,1.0/36.0,1.0/36.0};
 int cx[]={0,1,0,-1,0,1,-1,-1,1};
 int cy[]={0,0,1,0,-1,1,1,-1,-1};
 int compliment[]={0,3,4,1,2,7,8,5,6};
+double wxx[] = {0.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+double wyy[] = {0.0, -1.0/6.0, 1.0/3.0, -1.0/6.0, 1.0/3.0, -1.0/24.0, -1.0/24.0, -1.0/24.0, -1.0/24.0};
+double wxy[] = {0.0, 0.0, 0.0, 0.0, 0.0, 1.0/4.0, -1.0/4.0, 1.0/4.0, -1.0/4.0};
+
[…]

### 2012-02-14 Symmetric/binary.cpp
Added calculation of the mass.

@@ -635,6 +635,14 @@ void stream()
 	
 }
 
+void calculate_mass()
+{
+	double mass=0.0;
+	for(int counter=0;counter<NUM;counter++)
+		if (geometry[counter]==1)
+			mass+=phi[counter];
+	std::cout<<"Mass is "<<mass<<"\n";
+}
 
 int main(int argc, char* argv[])
 {
@@ -651,8 +659,10 @@ int main(int argc, char* argv[])
 		stream();
         
 	    if (counter%NSIGNAL==0)
+	    {
 	    	std::cout<<"Counter="<<counter<<"\n";
-    
+    		calculate_mass();
+    	}
 		//Writing files
 		if (counter%NOUTPUT==0)
 		{

### 2012-02-16 Symmetric/binary_wall.cpp
Running 300 cases.

@@ -25,10 +25,10 @@ int NSIGNAL=100;
 
 //Other constants
 const int NPOP=9;
-const int radius=50;
+const int radius=80;
 int radius_droplet=10;
-double wall_gradient=-0.05;
-const int NUM_DROPLETS=3;
+double wall_gradient=-0.1;
+const int NUM_DROPLETS=4;
 const int angle=360/NUM_DROPLETS;
 const double pi=4.0*std::atan(1.0);
 
@@ -231,6 +231,7 @@ void init()
 	//Bulk nodes initialization
 	double feq;
 	double geq;
+	double sum;
 	
 	for(int iY=0;iY<NY;iY++)
 		for(int iX=0;iX<NX;iX++)
@@ -419,8 +420,8 @@ void update_phase()
         phase_temp=0.0;
         if (geometry[counter]==1)
         {
-        	for(int k=0;k<NPOP;k++)
-        		phase_temp+=g[counter*NPOP+k];
+ 	    	for(int k=0;k<NPOP;k++)
+ 	       		phase_temp+=g[counter*NPOP+k];
         	phi[counter]=phase_temp;
 		}
 	}
@@ -428,7 +429,7 @@ void update_phase()
 	for(int counter=0;counter<bb_nodes.size();counter++)
 	{
 		int dir=main_dir[counter];
-		int counter2=bb_nodes[counter]+cy[dir]*NX+cx[dir];
+		int counter2=bb_nodes[counter]+cy[main_dir[counter]]*NX+cx[main_dir[counter]];
 		phi[bb_nodes[counter]]=phi[counter2]-wall_gradient;
 	}
 	
@@ -451,7 +452,7 @@ void initialize_geometry()
 		int iX=counter%NX;
 		int iY=counter/NX;
 	    
-	    if ((iX-(NX-1)/2)*(iX-(NX-1)/2)+(iY-(NY-1)/2)*(iY-(NY-1)/2)<radius*radius)
+	    if ((abs(iX-(NX-1)/2)<radius) && (abs(iY-(NY-1)/2)<radius))
 	    	geometry[counter]=-1;
 	    else
 	    	geometry[counter]=1;  
@@ -503,8 +504,8 @@ void initialize_geometry()
 		bool flag_droplet=false;
 		for (int counter_droplet=0;counter_droplet<NUM_DROPLETS;counter_droplet++)
 		{	
-			double center_x=(NX-1)/2-std::sin(angle*(counter_droplet-1)*pi/180.0)*(radius_droplet+radius);
[…]

### 2012-02-16 Symmetric/copy_to_checkers.py

@@ -1,0 +1,17 @@
+import numpy
+import os
+import subprocess
+
+def copy_files():
+    subprocess.call(['scp','binary.cpp','shurik@checkers.westgrid.ca:/home/shurik/ComplicatedBunch/'])
+    subprocess.call(['scp','binary_wall.cpp','shurik@checkers.westgrid.ca:/home/shurik/ComplicatedBunch/'])
+    subprocess.call(['scp','govern.py','shurik@checkers.westgrid.ca:/home/shurik/ComplicatedBunch/'])
+    subprocess.call(['scp','binary.pbs','shurik@checkers.westgrid.ca:/home/shurik/ComplicatedBunch/'])
+    subprocess.call(['scp','binary_wall.pbs','shurik@checkers.westgrid.ca:/home/shurik/ComplicatedBunch/'])
+
+if __name__=="__main__":
+    #modify_file()
+    #run_simulations()
+    #copy_files("42",5,4)
+    #copy_files("60",10,5)
+    copy_files()

### 2012-02-16 Symmetric/govern.py

@@ -1,0 +1,60 @@
+#import numpy
+import os
+import subprocess
+def modify_file(radius_str,wall_gradient_str):
+    f=open("binary.pbs","r+")
+    f2=open("binary_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE1",radius_str)
+            line=line.replace("TOCHANGE2",wall_gradient_str)
+        f2.write(line)
+            
+    f.close()
+    f2.close()
+
+def modify_file_wall(radius_str,wall_gradient_str):
+    f=open("binary_wall.pbs","r+")
+    f2=open("binary_wall_new.pbs","w")
+    for counter,line in enumerate(f):
+        if line.find("TOCHANGE")!=-1:
+            line=line.replace("TOCHANGE1",radius_str)
+            line=line.replace("TOCHANGE2",wall_gradient_str)
+        f2.write(line)
+            
+    f.close()
+    f2.close()
+
+
+def run_simulations():
+    radii_str=[str(x) for x in range(5,40,5)]
+
+    for radius_str in radii_str:
+        subprocess.call(['mkdir','-p',radius_str])
+        subprocess.call(['cp','main.out',radius_str+"/"])
+        subprocess.call(['cp','main_wall.out',radius_str+"/"])
+        subprocess.call(['cp','binary.pbs',radius_str+"/"])
+        subprocess.call(['cp','binary_wall.pbs',radius_str+"/"])
+        os.chdir(radius_str)
+        wall_gradients_str=["Grad"+str(x) for x in range(-45,50,5)]
+        wall_gradients=[str(x) for x in range(-45,50,5)]
+        
+        for wall_counter,wall_gradient_str in enumerate(wall_gradients_str):
+            subprocess.call(['mkdir','-p',wall_gradient_str])
+            subprocess.call(['cp','main.out',wall_gradient_str+"/"])
+            subprocess.call(['cp','main_wall.out',wall_gradient_str+"/"])
+            subprocess.call(['cp','binary.pbs',wall_gradient_str+"/"])
+            subprocess.call(['cp','binary_wall.pbs',wall_gradient_str+"/"])
+            os.chdir(wall_gradient_str)
+            wall_gradient=0.01*float(wall_gradients[wall_counter])
+            modify_file(radius_str,str(wall_gradient))
+            modify_file_wall(radius_str,str(wall_gradient))
[…]

### 2012-08-23 Text/paper.tex
Minor changes.
Added proposed paper conclusion ppt file containing some figures and guide to paper writing

@@
 \documentclass{article}
-\title{Binary fluid simulations with complicated geometries}
+\title{Conditions for successful wetting during collision between emulsion droplets and curved substrate}
 \begin{document}
 \maketitle
-We will start description here.
+\section{conclusions}
+The work presented investigates the interaction between emulsion droplets and curved substrates to understand the critical factors controlling the efficiency and the kinetics of the wetting process during collision.
+We use 2D Lattice Boltzmann methods to simulate spherical emulsion droplets colliding on a curved "cylindrical" substrate.
+The properties of the substrate are set by controlling its curvature and the three phase contact angle with the emulsion droplet and the surrounding fluid.
+The emulsion droplet is characterized by its size, viscosity and interfacial tension with the surrounding fluid.
+As expected we observe that the curvature of the droplet or substrate and the kinetics of the collision process does not effect the equilibrium three phase contact angle after wetting.
+However a detailed analysis of the collision process reveals that droplets deformation at wetting critically depends on the collision speed and relative dimension of droplet and substrate.
+Large droplets approaching the substrate very slowly deform very mildly before wetting while during fast collision a higher deformation is achieved before wetting occurs.
+For small droplets the same trend is found but overall smaller deformation are observed.
+The results can be rationalized if we consider a hydrodynamic disjoining pressure that retard contact between droplets and substrate.
+Based on this finding we can map the optimal conditions to achieve successful wetting, deposition and retention of an emulsion droplet on a substrate.
+This results can be used to guide the design of emulsions used as actives delivery vehicles.
+Emulsion size and interfacial properties can be tuned to optimize deposition efficiency on the relevant substrates based on the hydrodynamic parameters of the collision process.
+Such information are of important practical utility in farmaceutical and cosmetic application in which emulsion droplets are often used to deposit active ingredient on tissues or fibers.
 \end{document}

### 2012-09-05 Text/paper.tex
Started putting LBM part to the paper.

@@
 \documentclass{article}
+\usepackage{amsmath,amssymb}
+\usepackage{bm}
+\usepackage[numbers,sort&compress]{natbib}
+\usepackage{color}
+\usepackage{graphicx}
+
+\newcommand{\Ca}{\mathrm{Ca}}
+\newcommand{\beq}{\begin{equation}}
+\newcommand{\feq}{\end{equation}}
+\newcommand{\beqal}{\begin{equation}\begin{aligned}}
+\newcommand{\feqal}{\end{aligned}\end{equation}}
+
 \title{Conditions for successful wetting during collision between emulsion droplets and curved substrate}
@@
 \maketitle
-\section{conclusions}
+
+\section{Binary-liquid lattice Boltzmann model}
+{\color{red} This text was taken from the old text and needs to be modified}
+
+The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
+physical domain. It utilizes
+probability distribution functions (also known as particle populations)
+containing information about
+macroscopic variables, such as fluid density and momentum. LBE consists of
+two parts: a local collision step, and a propagation step which transports
+information from one node to another along some 
+directions specified by the discrete velocity set.
+The LBE is typically implemented as follows:
+\begin{equation}
+\label{standard:implementation}
+\begin{aligned}
+&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) +
+F_i,&&\text{ collision step}\\
+&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{ propagation step}, 
+\end{aligned}
+\end{equation}
+where $f_i$ is the probability distribution function in the direction $\bm{c_i}$,
+ $f_i^{eq}$ is the equilibrium probability distribution function, $\omega$ is the
+relaxation parameter, and $F_i$ is the external force population. The force population
+represents an external physical force and is implemented in the current work using the scheme
+outlined in \citet{guo}.
+
+The binary fluid LB model is
+based on a free-energy functional \cite{swift,landau}, and operates with two
+sets of populations: one to track the pressure and the velocity fields, and another to represent the
+phase field $\phi$ indicating the gas or liquid.
+
+The model we use is a two-dimensional nine-velocity (D2Q9) model,
+with equilibrium populations \cite{pooley-contact}:
+\begin{equation}
+\label{set:equilibrium:binary}
+\begin{aligned}
+&f_i^{eq}&&=w_i 
+\biggl(3
+p_0 - k \phi \Delta \phi
++\rho\frac{u_{\alpha}c_{i\alpha}}{c_s^2}+\rho \frac{Q_{i\alpha\beta}u_{\alpha } u_ {
+\beta}}{2 c_s^4}\biggr)\\
+&&&+k\bigl(w_i^{xx} (\partial_x \phi)^2+w_i^{yy} (\partial_y \phi)^2 +w_i^{xy} \partial_x
+\phi \partial_y \phi \bigr), 1\leq i \leq 8\\
+&f_0^{eq}&&=\rho-\sum_{i\neq0}{f_i^{eq}}\\
+&g_i^{eq}&&=w_i\left(\Gamma \mu + \phi\frac{ c_{i\alpha} u_{i\alpha}}{c_s^2}+\phi
+\frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}\right), 1\leq i \leq 8 \\
+&g_0^{eq}&&=\phi-\sum_{i\neq0}{g_i^{eq}}\quad,
+\end{aligned}
+\end{equation}
+where $\Gamma$ is the mobility parameter; the chemical potential
+$\mu=-A\phi+A\phi^3-k\Delta\phi$; $k$ is the parameter related to the surface
+tension; $A$ is the parameter of the free-energy model. The bulk pressure
+is expressed as $p_0=c_s^2 \rho +A (-0.5 \phi^2+0.75 \phi^4)$ with
+the sound speed $c_s^2=1/3$. 
+Parameters specific to the D2Q9 grid are the weights
+$w_i=\left\{\frac{4}{9},\frac{1}{9},\frac{1}{9},\frac{1}{9},\frac{1}{9},
+\frac{1}{36},\frac{1}{36},\frac{1}{36},\frac{1}{36}\right\}$, and the tensor
+$Q_{i\alpha\beta}=c_{i\alpha} c_{i\beta} - c_s^2 \delta_{\alpha\beta}$.  
+Other weights 
+%related to the
+%inclusion of the surface tension coefficient into the equations 
+are as follows:
+$w^{xx}_{1-2}=w^{yy}_{3-4}=1/3$, $w^{xx}_{3-4}=w^{yy}_{1-2}=-1/6$,
+$w^{xx}_{5-8}=w^{yy}_{5-8}=-1/24$, $w^{xy}_{1-4}=0$, $w^{xy}_{5-6}=1/4$ and
+$w^{xy}_{7-8}=-1/4$. The set of equations (\ref{set:equilibrium:binary}) restores the
+macroscopic
+fluid equations as:
+\begin{equation}
+\begin{aligned}
+&\partial_t \rho+ \partial_{\alpha} \rho u_{\alpha}=0\\
+&\rho\left(\partial_t+u_{\beta}\partial_{\beta}\right) u_{\alpha}= F_{\alpha}
+-\partial_{\beta}P_{\alpha \beta} +
+\nu\partial_{\beta}\left(\partial_{\alpha}u_{\beta}+\partial_{\beta} u_{\alpha}\right)\\
+&\partial_t \phi + \partial_{\alpha} \phi u_{\alpha}=M \partial^2_{\beta\beta} \mu,
+\end{aligned}
+\label{binary:fluid:system}
+\end{equation}
+where $\nu=c_s^2 (\tau-1/2)$ is the viscosity,
+$M=\Gamma(\tau_{\phi}-1/2)$ is the mobility parameter, and $\tau=\frac{1}{\omega}$ and $\tau_{\phi}$
+are the relaxation parameters of density and phase fields, 
+$P_{\alpha\beta}=\Bigl(p_0-k\phi \Delta \phi -\frac{k}{2}|\nabla \phi|^2\Bigr)\delta_{\alpha\beta}
++ k \partial_{\alpha} \phi \partial_{\beta} \phi$  \cite{pooley-contact}.The interface tension value
+in the framework of the binary liquid model is $\gamma=\sqrt{\frac{8 k
+A}{9}}$. The inclusion of the interface tension in the momentum flux tensor is done through the
+coefficients $k$, $A$ and weights $w_i^{\alpha\beta}$.
+
+Note that the first equation of system \ref{standard:implementation} simulates the continuity and
+the Navier-Stokes equations, i.e. the first two equations in (\ref{binary:fluid:system}). The second
+equation
+of system \ref{standard:implementation} simulates the phase governing equation, i.e. the third
+equation in
+(\ref{binary:fluid:system}). The system (\ref{binary:fluid:system}) allows the separation of the
+liquid
+phase with $\phi=1$ and a so-called gas phase with $\phi=-1$. The
+relaxation time is taken as linearly dependent on the relaxation
+times $\tau_{\mathrm{gas}}$ and $\tau_{\mathrm{liq}}$:
+$\tau=\tau_{\mathrm{gas}}+\frac{\phi+1}{2}(\tau_{\mathrm{liq}}-\tau_{\mathrm{gas}})$. This allows
+to change viscosity from the gas viscosity
+$\nu_{\mathrm{gas}}=\frac{1}{3}\Bigl(\tau_{\mathrm{gas}}-\frac{1}{2}\Bigr)$ to the liquid viscosity
+$\nu_{\mathrm{liq}}=\frac{1}{3}\Bigl(\tau_{\mathrm{liq}}-\frac{1}{2}\Bigr)$ while phase changes
+accordingly.
+
+While the lattice Boltzmann system has parameters such as the surface tension, the gas and liquid
+viscosities, etc., those parameters are not the representative and
+proportional quantities of the parameters in a physical system. The parameters of the lattice
+Boltzmann are connected with the physical parameters only through the non-dimensional
+numbers governing the physics of the problem. In our case, these numbers are the capillary number $\Ca$ and the
+viscosity ratio $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}$, which are
+obtained from the physical world and then matched through the lattice Boltzmann quantities.
+ The set of
+the fluid and phase equations \eqref{binary:fluid:system} is valid in the lattice Boltzmann space
+and in the physical domain. Therefore, one can substitute any quantity, i.e.
+$U_{\mathrm{bubble}}$, in the physical units or in the lattice Boltzmann units as soon as the
+capillary number is the same in both worlds.
+\section{Boundary conditions}
+In binary-liquid model It is known that the equilibrium contact angle $\theta_{w}$ of a droplet located at a flat surface depends on the phase gradient through the complicated relation \cite{briant-contact-line}:
+\beqal
+&k \partial_{\perp} \phi = - h
+&\sqrt{\frac{2}{k A}}h= 2 \mathrm{sign}\biggl(\frac{\pi}{2}-\theta_w\biggr) \biggl[\cos\Bigl(\frac{\alpha}{3}\Bigr)\Bigl(1-\cos\Bigl(\frac{\alpha}{3}\Bigr)\Bigr)\biggr]\\
+&\cos(\alpha)=\sin^2(\theta_w),
+\feqal
+where $\theta_w$ is the contact angle, $\partial_{\perp}\phi$ is the imposed phase gradient at the wall.
+From this equation one can find the contact angle as the function of the phase gradient at the wall, $\theta_w=\theta_w(\partial_{\perp}\phi)$.
+
+According to works \cite{manukyan-curved,carrol-curved} the contact angle at the curved substrate should have the same value as in the flat case.
+This case is validation case for the lattice Boltzmann simulations.
+The challenge is to impose certain phase gradient at the curved substrate.
+The lattice Boltzmann system operates on the rectangular grid and one needs to come up with simple and elegant numerical stencil to impose the phase gradient in the direction of the normal to curved substrate.
+{\color{red} Put here explanation and reference to japanese work - plus validation case with all graphs.}
+We present new boundary conditions to fix the angle at the surface.
+
+\section{Conclusions}
 The work presented investigates the interaction between emulsion droplets and curved substrates to understand the critical factors controlling the efficiency and the kinetics of the wetting process during collision.
@@
 Emulsion size and interfacial properties can be tuned to optimize deposition efficiency on the relevant substrates based on the hydrodynamic parameters of the collision process.
-Such information are of important practical utility in farmaceutical and cosmetic application in which emulsion droplets are often used to deposit active ingredient on tissues or fibers.
+Such information are of important practical utility in pharmaceutical and cosmetic application in which emulsion droplets are often used to deposit active ingredient on tissues or fibers.
+\bibliographystyle{unsrt}
+\bibliography{paper}
 \end{document}

### 2012-09-05 Pressure/analyze.py

@@ -317,14 +317,61 @@ def compare_with_initial():
     pylab.legend(["Pressures_F1","Pressures_F5","Init_pressures","Init_pressures_bef_collision_F5"])
     pylab.savefig("comparison_another_approach.eps",dpi=300)
 
+def make_nice_graphs():
+    file_list=["vtk0035000_R10_Grad-20_F1.vtk","vtk0034000_R20_Grad-20_F1.vtk",
+               "vtk0033000_R30_Grad-20_F1.vtk","vtk0033000_R40_Grad-20_F1.vtk",
+               "vtk0032000_R50_Grad-20_F1.vtk"]
+    file_list=["vtk0020000_R10_Grad-20_F5.vtk","vtk0020000_R20_Grad-20_F5.vtk",
+               "vtk0020000_R30_Grad-20_F5.vtk","vtk0020000_R40_Grad-20_F5.vtk",
+               "vtk0020000_R50_Grad-20_F5.vtk"]
+    #file_list=["vtk0035000_R10_Grad-20_F1.vtk","vtk0036000_R10_Grad-20_F1.vtk",
+    #          "vtk0034000_R20_Grad-20_F1.vtk","vtk0035000_R20_Grad-20_F1.vtk",
+    #          "vtk0033000_R30_Grad-20_F1.vtk","vtk0034000_R30_Grad-20_F1.vtk",
+    #          "vtk0033000_R40_Grad-20_F1.vtk","vtk0034000_R40_Grad-20_F1.vtk",
+    #          "vtk0033000_R50_Grad-20_F1.vtk","vtk0032000_R50_Grad-20_F1.vtk"]    		   
+    #file_list=["vtk0020000_R10_Grad-20_F5.vtk","vtk0021000_R10_Grad-20_F5.vtk",
+    #           "vtk0020000_R20_Grad-20_F5.vtk","vtk0021000_R20_Grad-20_F5.vtk",
+    #           "vtk0020000_R30_Grad-20_F5.vtk","vtk0021000_R30_Grad-20_F5.vtk",
+    #           "vtk0020000_R40_Grad-20_F5.vtk","vtk0021000_R40_Grad-20_F5.vtk",
+    #           "vtk0020000_R50_Grad-20_F5.vtk","vtk0021000_R50_Grad-20_F5.vtk"]    		   
 
+    #styles=['ks','ko','k+','kD','k*','kH','kv','k^','kh','k-']
+    
[…]

### 2012-10-01 Text/paper.tex
Next iteration. Added a few pictures  - need to add geometrical stuff.

@@
 \section{Binary-liquid lattice Boltzmann model}
-{\color{red} This text was taken from the old text and needs to be modified}
-
 The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
@@
 containing information about
-macroscopic variables, such as fluid density and momentum. LBE consists of
+macroscopic variables, such as fluid density, momentum, and the phase order parameter for multiphase models. LBE consists of
 two parts: a local collision step, and a propagation step which transports
@@
 Other weights 
-%related to the
-%inclusion of the surface tension coefficient into the equations 
 are as follows:
@@
 $w^{xx}_{5-8}=w^{yy}_{5-8}=-1/24$, $w^{xy}_{1-4}=0$, $w^{xy}_{5-6}=1/4$ and
-$w^{xy}_{7-8}=-1/4$. The set of equations (\ref{set:equilibrium:binary}) restores the
+$w^{xy}_{7-8}=-1/4$.
+
+One can show that the set of discrete evolution equations (\ref{set:equilibrium:binary}) restores the
 macroscopic
-fluid equations as:
+multiphase equations through the Chapman-Enskog analysis \cite{chapman}:
 \begin{equation}
@@
 
-While the lattice Boltzmann system has parameters such as the surface tension, the gas and liquid
-viscosities, etc., those parameters are not the representative and
-proportional quantities of the parameters in a physical system. The parameters of the lattice
-Boltzmann are connected with the physical parameters only through the non-dimensional
-numbers governing the physics of the problem. In our case, these numbers are the capillary number $\Ca$ and the
-viscosity ratio $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}$, which are
-obtained from the physical world and then matched through the lattice Boltzmann quantities.
- The set of
-the fluid and phase equations \eqref{binary:fluid:system} is valid in the lattice Boltzmann space
-and in the physical domain. Therefore, one can substitute any quantity, i.e.
-$U_{\mathrm{bubble}}$, in the physical units or in the lattice Boltzmann units as soon as the
-capillary number is the same in both worlds.
+Note that the parameters of the lattice
+Boltzmann model, as the surface tension, viscosity, etc are connected with the physical parameters only through the non-dimensional
+numbers governing the physics of the problem.  Therefore, the parameters in the lattice Boltzmann system have certain degree of freedom and not proportional to the physical parameters.
+
 \section{Boundary conditions}
-In binary-liquid model It is known that the equilibrium contact angle $\theta_{w}$ of a droplet located at a flat surface depends on the phase gradient through the complicated relation \cite{briant-contact-line}:
+There are a number of boundary conditions in the lattice Botlzmann system, as bounce-back \cite{yu}, Zou-He pressure and velocity boundary conditions \cite{zouhe-boundary}, Inamuro boundary conditions \cite{inamuro-scalar-boundary}.
+The lattice Boltzmann model operates with discrete populations and on the rectangular grid.
+That brings certain challenges to match boundary conditions imposed on the macroscopic variables to the discrete populations world.
+
+The current work simulates the deposition of the droplet to the curved substrate.
+The multiphase system has the following macroscopic properties: density, velocity, surface tension and phase order parameter.
+In order to be able to change the contact angle, on needs to impose the boundary condition on the phase gradient normal to the wall.
+For example, the equilibrium contact angle $\theta_{w}$ of a droplet located at a flat surface depends on the phase gradient normal to the surface through the complicated relation \cite{briant-contact-line}:
 \beqal
-&k \partial_{\perp} \phi = - h
+&k \partial_{\perp} \phi = -h\\
 &\sqrt{\frac{2}{k A}}h= 2 \mathrm{sign}\biggl(\frac{\pi}{2}-\theta_w\biggr) \biggl[\cos\Bigl(\frac{\alpha}{3}\Bigr)\Bigl(1-\cos\Bigl(\frac{\alpha}{3}\Bigr)\Bigr)\biggr]\\
@@
 From this equation one can find the contact angle as the function of the phase gradient at the wall, $\theta_w=\theta_w(\partial_{\perp}\phi)$.
+Fig.
+\ref{fig:equilibrium:droplet:curved} shows the dependance of the equilibrium angle depending on the phase gradient normal to the flat wall.
 
-According to works \cite{manukyan-curved,carrol-curved} the contact angle at the curved substrate should have the same value as in the flat case.
-This case is validation case for the lattice Boltzmann simulations.
-The challenge is to impose certain phase gradient at the curved substrate.
+The topic of this work is the deposition of the droplet to the curved substrate.
+According to works \cite{manukyan-curved,carroll-curved} the contact angle at the curved substrate remains the same as in the flat case.
+However, the challenge is to impose certain phase gradient at the curved substrate.
 The lattice Boltzmann system operates on the rectangular grid and one needs to come up with simple and elegant numerical stencil to impose the phase gradient in the direction of the normal to curved substrate.
+
+For example, the work \cite{japan-curved} impose the constat phase value at all solid nodes (instead of constant phase gradient) to calculate the laplacian used in the equilibrium function which drives free energy to have certain contact angle at the surface.
+However, we feel that this approach is suitable for the equilibrium steady-state approaches, but for the dynamic situation to capture transient phenomena one needs to impose the constant phase gradient value at solid nodes.
+
+The suggested "easy-to-implement" algorithm uses the mirror boundary conditions. Figure \ref{fig:free:surface} shows the staircase approximation of the curved boundaries. 
+Thus, the normal to the boundary which
+is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}.  Imposing the
+symmetric boundary conditions requires $\phi_{n,F}$=$\phi_{n,B}+\partial_{\perp} \phi$.
+For any solid boundary nodes, the normal to the staircase approximation was calculated and the phase value was assigned according to the latter equation.
+In terms of population, to conserve the mass in the phase domain we used ea  the latter equation can give the value to impose for the calculation of the laplacian and $U_{\tau,F}=U_{\tau,B}$.
+We can copy poptul
+populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
+$c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and
+$c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and
+$c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.  
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
+\caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
+Boundary nodes are depicted by crosses, and fluid nodes are represented by dots.
+One imposes only phase values at the nodes to calculate laplacians used in the equilibrium functions.
+In the population space, one uses the bounce-back rule \cite{yu-viscous}, which conserves mass.
+\label{fig:free:surface}}
+\end{figure}
+
+{\color{red} Include here simple pictures of droplet on curved interface.}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
+\caption{Stair-case approximation to the curved substrate. The incoming populations \label{fig:free:surface}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{Figures/main_curve_circle.eps}
+\caption{Equilibrium angles at the curved substrate.
+One can see that the contact angle at the curved substrate mimics the analytically calculated contact angle at the flat substrate.
+\label{fig:equilibrium:droplet:curved}}
+\end{figure}
+
+One of the suggested 
 {\color{red} Put here explanation and reference to japanese work - plus validation case with all graphs.}
 We present new boundary conditions to fix the angle at the surface.
+
+Therefore, for the flat case one needs to be able to impose the phase gradient at a curved substrate, $\partial_{\perp}\phi$.
+One needs to represent this boundary condition  For the lattice Boltzmann method operating on the rectangular grid with populat
 

### 2012-10-01 Symmetric/process.py

@@ -344,17 +344,36 @@ def circle_analysis():
         theor.append(180.0/math.pi*fsolve(f,math.pi/120*counter,args=(grad)))   
     pylab.figure(1)    
     angles=numpy.array(angles)    
-    pylab.plot(0.01*gradients,angles[:,0],"k+")
-    pylab.plot(0.01*gradients,angles[:,1],"ko")
-    pylab.plot(0.01*gradients,angles[:,2],"ks")
-
-    
-    pylab.plot(grads,theor,"+")
+    #pylab.plot(0.01*gradients,angles[:,0],"k+")
+    #pylab.plot(0.01*gradients,angles[:,1],"ko")
+    gradients=0.01*gradients
+    pylab.plot(gradients,angles[:,2],"ko",markersize=8)
+    theor=numpy.array(theor)
+    good_ind=numpy.where(numpy.logical_and(theor>5,theor<170))
+    theor=theor[good_ind]
+    grads=grads[good_ind]
+    pylab.plot(grads,theor,"k-",linewidth=3)
+    numpy.savetxt("theoretical.dat",zip(grads.tolist(),theor.tolist()))
+    numpy.savetxt("circle.dat",zip(gradients.tolist(),angles[:,2].tolist()))
+  
     pylab.ylim(ymin=0.0,ymax=180.0)
     pylab.savefig("main_curve_circle.eps",format="EPS",dpi=300.0)
+    pylab.legend(["Analytical","Simulations"])
     pylab.figure(99)
     pylab.savefig("different_boxes_circle.eps",format="EPS",dpi=300.0)
 
+def circle_figures():
+    anals=numpy.loadtxt("theoretical.dat")
+    sims=numpy.loadtxt("circle.dat")
+    pylab.plot(anals[:,0],anals[:,1],"k-",linewidth=3)
+    pylab.plot(sims[:,0],sims[:,1],"ko",markersize=8)
+    pylab.legend(["Analytical","Simulations"])
+    pylab.ylim(ymin=0.0,ymax=180.0)
+    pylab.xlabel(r'''$\partial_{\perp}\phi$''',fontsize=20)
+    pylab.ylabel(r'''$\theta_{w}$''',fontsize=20)
+    pylab.savefig("main_curve_circle.eps",format="EPS",dpi=300.0)
+    pylab.title("Contact angle",fontsize=30)
+    
 if __name__=="__main__":
     #file_name="vtk_wall0010000.vtk"    
[…]

### 2012-10-02 Text/paper.tex
More details about initial angle on a substrate.

@@
 
-The suggested "easy-to-implement" algorithm uses the mirror boundary conditions. Figure \ref{fig:free:surface} shows the staircase approximation of the curved boundaries. 
-Thus, the normal to the boundary which
-is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}.  Imposing the
+The suggested algorithm uses the mirror boundary conditions. Figure \ref{fig:free:surface} shows the staircase approximation of the curved boundaries. 
+Thus, the normal to the boundary is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}.  Imposing the
 symmetric boundary conditions requires $\phi_{n,F}$=$\phi_{n,B}+\partial_{\perp} \phi$.
 For any solid boundary nodes, the normal to the staircase approximation was calculated and the phase value was assigned according to the latter equation.
-In terms of population, to conserve the mass in the phase domain we used ea  the latter equation can give the value to impose for the calculation of the laplacian and $U_{\tau,F}=U_{\tau,B}$.
-We can copy poptul
-populations in the certain order to do it, for example $f_{B,i}=f_{F,\bar{i}}$, where $c_i$ and
-$c_{\bar{i}}$ are complementary directions, where $c_{i,n}=-c_{\bar{i},n}$ and
-$c_{i,\tau}=c_{\bar{i},\tau}$, where $c_{i,n}=(\bm{c_i} \cdot \bm{n})\bm{n}$ and
-$c_{i,\tau}=\bm{c_i}-(\bm{c_i}\cdot \bm{n})\bm{n}$.  
+In terms of population, to conserve the mass in the phase domain we used the bounce-back condition which conserves the mass \cite{yu}.
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
+\includegraphics[width=\textwidth]{Figures/free_surface.eps}
 \caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
@@
 One imposes only phase values at the nodes to calculate laplacians used in the equilibrium functions.
-In the population space, one uses the bounce-back rule \cite{yu-viscous}, which conserves mass.
+In the population space, one uses the bounce-back rule \cite{yu}, which conserves mass.
 \label{fig:free:surface}}
 \end{figure}
-
-{\color{red} Include here simple pictures of droplet on curved interface.}
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
-\caption{Stair-case approximation to the curved substrate. The incoming populations \label{fig:free:surface}}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\textwidth]{Figures/main_curve_circle.eps}
+\includegraphics[width=0.5\textwidth]{Figures/droplet_shapes_curved_substrates.eps}
+\includegraphics[width=0.5\textwidth]{Figures/main_curve_circle.eps}\\
 \caption{Equilibrium angles at the curved substrate.
@@
 \end{figure}
-
-One of the suggested 
-{\color{red} Put here explanation and reference to japanese work - plus validation case with all graphs.}
-We present new boundary conditions to fix the angle at the surface.
-
-Therefore, for the flat case one needs to be able to impose the phase gradient at a curved substrate, $\partial_{\perp}\phi$.
-One needs to represent this boundary condition  For the lattice Boltzmann method operating on the rectangular grid with populat
 

### 2012-10-02 Symmetric/process.py

@@ -247,8 +247,13 @@ def read_file_circle(file_name):
 
     #return 180.0/math.pi*math.atan2(vecy,vecx)
 
+gl_counter=0
+
 def read_file_circle_clean(file_name):
-    radius=50    
+    radius=50
+    global gl_counter
+    gl_counter=gl_counter+1
+    styles=["k+","ko","ks","kv","k^","kd","kD","kh"]    
 
     gridreader = vtk.vtkStructuredGridReader() 
     gridreader.SetFileName(file_name)
@@ -296,6 +301,23 @@ def read_file_circle_clean(file_name):
     newy=numpy.roll(newy,-counter)
     print counter
     
+    pylab.figure(100)
+    dist=0.0
+    while dist<10:
+        dist=(newx[counter+1]-newx[counter])**2+(newy[counter+1]-newy[counter])**2
+        counter=counter+1
+    
+    pylab.plot(newx[:counter],newy[:counter],"k--",linewidth=3)
+    if gl_counter<2:
+        pylab.plot(coor_wall[:,0],coor_wall[:,1],"k-",linewidth=3)
+    pylab.ylabel(r'''$y$''',fontsize=20)
+    pylab.xlabel(r'''$x$''',fontsize=20)
+    pylab.ylim((60,240))
+    pylab.xlim((60,240))
+    pylab.title("Droplet shapes on a curved substrate",fontsize=20)
+    pylab.savefig("droplet_shapes_curved_substrates",format="EPS")
+    
+    pylab.figure(99)
     #calculate vector
     shift=3
     angles=[]
@@ -332,7 +354,7 @@ def read_file_circle_clean(file_name):
 
 def circle_analysis():
     angles=[]
-    gradients=numpy.arange(-40,40,5)
+    gradients=numpy.arange(-40,41,10)
     
     for gradient in gradients:
         file_name="20/Grad"+str(gradient)+"/vtk0020000.vtk"
@@ -381,6 +403,6 @@ if __name__=="__main__":
 
     file_name="20/Grad-35/vtk0020000.vtk"
     #read_file_circle(file_name)
-    #circle_analysis()
-    circle_figures()
+    circle_analysis()
+    #circle_figures()
     pylab.show()

### 2012-10-04 Text/paper mc edit.tex
my edit of the text file

--- 2012-10-02 Text/paper.tex
@@
 \maketitle
+\section{Abstract}
+\section{introduction}
+Emulsion droplets are often used a delivery vehicle to deposit active ingredients on target substrates in application such as drug delivery, cosmetics and detergent products.
+In order to fulfill their function emulsion formulation are optimized in terms of emulsion droplets size, stability, surface properties and interaction forces with the target substrate.
+Virtually the properties of the emulsion droplets while stored before their use and their behavior after wetting the target substrate can be finely designed using well established physical models that identify the critical parameters controlling stability and adhesion properties.
+
+However, to fulfill its function, the emulsion droplets need to be successfully transferred on the substrate.
+This transfer process, that involves the complex sequence of events that take the emulsion droplets from the formulated state to the substrate is not as well characterized and the role of the different parameters related to the emulsion, substrate and hydrodynamic interaction mediated by the continuous phase is still poorly defined.
+Recent AFM studied of emulsion interactions identified the critical role of hydrodynamic effect on the repulsion between two emulsions colliding at different speed.
+The effective disjointing pressure preventing contact and coalescence between the two emulsion droplets has an electrostatic and an hydrodynamic component.
+This suggest that also during the process of emulsion collision on a substrate successful contact and wetting of the surface critically depend on the interplay of the hydrodynamic and inter-facial properties.
+
+In this work we use Lattice Boltzmann simulation methods to study the effect of inter-facial and hydrodynamic parameters on the efficiency of the wetting process during collision.
+We simulate a spherical emulsion droplets colliding on a curved "cylindrical" substrate.
+The properties of the substrate are set by controlling its curvature and the three phase contact angle with the emulsion droplet and the surrounding fluid.
+The emulsion droplet is characterized by its size, viscosity and inter-facial tension with the surrounding fluid.
+The hydrodynamic properties are explored by simulating droplet collision on the substrate under different flow conditions.
+
+In the Next section we describe the idealized collision system simulated, the physical properties controlled in the simulation and the range of parameters explored (parameter space).
+In the following section we provide details about the simulation methods and its validation against other methodology previously proposed (Binary-liquid lattice Boltzmann model).
+Next we summarize the results of the parametric study focusing on the behavior of the emulsion as it collides with the substrate as a function of the interfacial and hydrodinamic parameters explored (Results).
+We then propose a map of the deposition efficiency within the explored parametric space (deposition efficiency map).
+Finally we summarize the results and relate to the related application areas (conclusions).
+
+\section{parameter space}
 
@@
 
-\section{Boundary conditions}
+\subsection{Boundary conditions}
 There are a number of boundary conditions in the lattice Botlzmann system, as bounce-back \cite{yu}, Zou-He pressure and velocity boundary conditions \cite{zouhe-boundary}, Inamuro boundary conditions \cite{inamuro-scalar-boundary}.
@@
 In terms of population, to conserve the mass in the phase domain we used the bounce-back condition which conserves the mass \cite{yu}.
-\begin{figure}
-\includegraphics[width=\textwidth]{Figures/free_surface.eps}
-\caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
-Boundary nodes are depicted by crosses, and fluid nodes are represented by dots.
-One imposes only phase values at the nodes to calculate laplacians used in the equilibrium functions.
-In the population space, one uses the bounce-back rule \cite{yu}, which conserves mass.
-\label{fig:free:surface}}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{Figures/droplet_shapes_curved_substrates.eps}
-\includegraphics[width=0.5\textwidth]{Figures/main_curve_circle.eps}\\
-\caption{Equilibrium angles at the curved substrate.
-One can see that the contact angle at the curved substrate mimics the analytically calculated contact angle at the flat substrate.
-\label{fig:equilibrium:droplet:curved}}
-\end{figure}
+
+%\begin{figure}
+%\includegraphics[width=\textwidth]{Figures/free_surface.eps}
+%\caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
+%Boundary nodes are depicted by crosses, and fluid nodes are represented by dots.
+One imposes only %phase values at the nodes to calculate laplacians used in the equilibrium functions.
+In the %population space, one uses the bounce-back rule \cite{yu}, which conserves mass.
+%\label{fig:free:surface}}
+%\end{figure}
+
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{Figures/droplet_shapes_curved_substrates.eps}
+%\includegraphics[width=0.5\textwidth]{Figures/main_curve_circle.eps}\\
+%\caption{Equilibrium angles at the curved substrate.
+One can see that the contact angle at the %curved substrate mimics the analytically calculated contact angle at the flat substrate.
+%\label{fig:equilibrium:droplet:curved}}
+%\end{figure}
+
+\section{Results}
+
+\section{Deposition efficiency map}
 

### 2012-10-04 Text/paper.tex

@@
 In terms of population, to conserve the mass in the phase domain we used the bounce-back condition which conserves the mass \cite{yu}.
+
 \begin{figure}
@@
 \end{figure}
+
 \begin{figure}
@@
 \end{figure}
+
+\section{Results}
+
+\section{Deposition efficiency map}
 

### 2012-10-23 SurfaceTension/analyze.py
New main figure.

@@ -170,6 +170,55 @@ def compare():
     pylab.plot([10,20,30,40,50],5*[numpy.mean(pressures)],"r-",linewidth=3)
     pylab.ylim(ymin=0)
 
+def compare_F5():
+    #ratio04=["vtk021000_R10_F5_R04.vtk","vtk022000_R10_F5_R04.vtk",
+    #         "vtk020000_R20_F5_R04.vtk","vtk021000_R20_F5_R04.vtk",
+    #         "vtk020000_R30_F5_R04.vtk","vtk021000_R30_F5_R04.vtk",
+    #         "vtk021000_R40_F5_R04.vtk","vtk022000_R40_F5_R04.vtk",
+    #         "vtk021000_R50_F5_R04.vtk","vtk022000_R50_F5_R04.vtk"]
+    #ratio07=["vtk020000_R10_F5_R07.vtk","vtk021000_R10_F5_R07.vtk",
+    #         "vtk020000_R20_F5_R07.vtk","vtk021000_R20_F5_R07.vtk",
+    #         "vtk020000_R30_F5_R07.vtk","vtk021000_R30_F5_R07.vtk",
+    #         "vtk020000_R40_F5_R07.vtk","vtk021000_R40_F5_R07.vtk",
+    #         "vtk020000_R50_F5_R07.vtk","vtk021000_R50_F5_R07.vtk"]
+    ratio13=["vtk020000_R10_F5_R13.vtk","vtk021000_R10_F5_R13.vtk",
+             "vtk019000_R20_F5_R13.vtk","vtk020000_R20_F5_R13.vtk",
+             "vtk019000_R30_F5_R13.vtk","vtk020000_R30_F5_R13.vtk",
+             "vtk019000_R40_F5_R13.vtk","vtk020000_R40_F5_R13.vtk",
+             "vtk019000_R50_F5_R13.vtk","vtk020000_R50_F5_R13.vtk"]
+             
+ 
+    file_list=ratio13
+    ending="ratio13"
+    pressures=[]
+    densities=[]
+    densities_one=[]
+    for file_name in file_list:
+        pressure,density,density_one=get_droplet("Force5/"+file_name,0.4)
+        pressures.append(pressure)
+        densities.append(density)
+        densities_one.append(density_one)
+        
+    numpy.savetxt("pressures_Grad-20_F5_"+ending+".txt",pressures)
[…]

### 2012-10-24 Text/paper.tex
updated paper

@@
 
-\title{Conditions for successful wetting during collision between emulsion droplets and curved substrate}
+\title{Conditions for successful wetting during collision between emulsion droplets and curved substrates}
 \begin{document}
@@
 \section{Abstract}
+In consumer products, cosmetics, and medicines many benefits are delivered by deposition of emulsion droplets onto hair, skin, or other tissues.
+The interaction of emulsion droplets with solid substrates is critical in determining the efficiency of delivery and can often be studied using the experiments with a model substrate like a fiber mesh.
+While numerous properties of emulsion droplets, like stability, size, interfacial tension, and adhesion can be varied, little is known about how each parameter influences the collision, wetting, and retention probability.
+The complex hydrodynamic interactions at play during the droplet deposition process must also be considered in addition to materials properties.
+In this work we use Lattice Boltzmann, LB, simulation methods to investigate such problems.
+The simultaneous need to simulate a multiphase system and flow through complex geometries makes LB simulation a good candidate for a parametric exploration of the effects of formulation and process parameters on deposition efficiency.
+We find that the condition for succesfull wetting upon collision critically depend on material properties such as relative size of droplet and substrate, interfacial tension and viscosity ratio.
+Additionally we find that also the hydrodinamic conditions play an important role to that can be rationalized considering the presence of an additional hydrodynamic disjoining pressure that depends on the collision speed.
+Based on this finding we can map the optimal conditions to achieve successful wetting, deposition and retention of an emulsion droplet on a substrate.
+This results can be used to guide the design of emulsions used as actives delivery vehicles.
+
+\pagebreak
 \section{introduction}
-Emulsion droplets are often used a delivery vehicle to deposit active ingredients on target substrates in application such as drug delivery, cosmetics and detergent products.
-In order to fulfill their function emulsion formulation are optimized in terms of emulsion droplets size, stability, surface properties and interaction forces with the target substrate.
+Emulsion droplets are often used as delivery vehicle to deposit active ingredients on target substrates in application such as drug delivery, cosmetics and detergent products.
+To fulfill their function, emulsion formulation are optimized in terms of emulsion droplets size, stability, surface properties and interaction forces with the target substrate.
 Virtually the properties of the emulsion droplets while stored before their use and their behavior after wetting the target substrate can be finely designed using well established physical models that identify the critical parameters controlling stability and adhesion properties.
-
-However, to fulfill its function, the emulsion droplets need to be successfully transferred on the substrate.
-This transfer process, that involves the complex sequence of events that take the emulsion droplets from the formulated state to the substrate is not as well characterized and the role of the different parameters related to the emulsion, substrate and hydrodynamic interaction mediated by the continuous phase is still poorly defined.
+However, the emulsion droplets need to be successfully transferred on the substrate and little is known on how to optimize this part of the delivery process.
+The deposition of the emulsion droplet involves the complex sequence of events that take the emulsion droplets from the formulated state to the substrate.
+This transfer process is not well characterized and the role of the different parameters related to the emulsion, substrate and hydrodynamic interaction mediated by the continuous phase is still poorly understood.
 Recent AFM studied of emulsion interactions identified the critical role of hydrodynamic effect on the repulsion between two emulsions colliding at different speed.
@@
 We then propose a map of the deposition efficiency within the explored parametric space (deposition efficiency map).
-Finally we summarize the results and relate to the related application areas (conclusions).
+Finally we summarize the results and discuss their relevance in the related application areas (conclusions).
 
+\pagebreak 
 \section{parameter space}
+While the detail of the simulation method will be given in the next section, here we describe the simple physical system that we simulate and the parameters explored.
 
+A droplet, dispersed phase, of dimension $R_e$ is placed at the beginning of a channel of fixed width $l_c$ and length $L_c$.
+The droplet is surrounded by a continuous liquid phase that fills the entire channel.
+In the simulation we can vary the relative viscosity between dispersed and continuous phase $\eta_r$ and the interfacial tension between the two phases $\gamma$.
+
+In the middle of the channel, downstream from the droplet position, we place a solid curved substrate with a circular cross section of radius $R_s$.
+The properties of the substrate surface can be tune to obtain a range of equilibrium three phase contact angles between the dispersed phase, continuous phase, and substrate surface $\eta_s$.
+
+At the beginning of the simulation, during the equilibration step,  a body force field is applied to the continuous phase to generate flow in the channel, while the flow field develops toward a steady state the droplet is held in the original position.
+The amplitude of the body force field can be varied to generate a range of hydrodynamic conditions for the collision process.
+
+Once the continuous phase flow is established the dispersed phase droplet is released and accelerates under the action of the body force and viscous forces toward the substrate, acceleration step.
+Since the droplet is placed in the middle of the channel relative to its width as for the substrate, the induced collision is a central collision.
+
+We describe the collision as a two step process.
+Initially during the collision pre-wetting stage, the droplets fell the presence of the substrate, applies a pressure on it, and deforms as the liquid layer of continuous phase that separate the droplet and substrate surface get depleted.
+
+Eventually contact between the two surfaces is produced, collision wetting stage, and the droplet wet the surface to reach an equilibrium position that depend on the balance between the interfacial forces and the hydrodynamic interaction with the continuous phase still in motion.
+
+Snapshots form a sumulation result representing the different step are represented in figure \ref{fig:simulation:explanation}
+
+\begin{figure}[h!]
+\includegraphics[width=1\textwidth]{Figures/collision_simulation.eps}
+\caption{Steps of the simulation of the collision process\label{fig:simulation:explanation}}
+\end{figure}
+
+\pagebreak 
 \section{Binary-liquid lattice Boltzmann model}
-The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
-physical domain. It utilizes
-probability distribution functions (also known as particle populations)
-containing information about
-macroscopic variables, such as fluid density, momentum, and the phase order parameter for multiphase models. LBE consists of
-two parts: a local collision step, and a propagation step which transports
-information from one node to another along some 
-directions specified by the discrete velocity set.
-The LBE is typically implemented as follows:
+The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the physical domain.
+It utilizes probability distribution functions (also known as particle populations) containing information about macroscopic variables, such as fluid density, momentum, and the phase order parameter for multiphase models.
+LBE consists of two parts: a local collision step, and a propagation step which transports information from one node to another along some
+directions specified by the discrete velocity set. The LBE is typically implemented as follows:
 \begin{equation}
@@
 where $f_i$ is the probability distribution function in the direction $\bm{c_i}$,
- $f_i^{eq}$ is the equilibrium probability distribution function, $\omega$ is the
-relaxation parameter, and $F_i$ is the external force population. The force population
-represents an external physical force and is implemented in the current work using the scheme
-outlined in \citet{guo}.
+ $f_i^{eq}$ is the equilibrium probability distribution function, $\omega$ is the relaxation parameter, and $F_i$ is the external force population.
+The force population represents an external physical force and is implemented in the current work using the scheme outlined in \citet{guo}.
 
-The binary fluid LB model is
-based on a free-energy functional \cite{swift,landau}, and operates with two
-sets of populations: one to track the pressure and the velocity fields, and another to represent the
-phase field $\phi$ indicating the gas or liquid.
-
-The model we use is a two-dimensional nine-velocity (D2Q9) model,
-with equilibrium populations \cite{pooley-contact}:
+The binary fluid LB model is based on a free-energy functional \cite{swift,landau}, and operates with two sets of populations: one to track the pressure and the velocity fields, and another to represent the phase field $\phi$ indicating the gas or liquid.
+The model we use is a two-dimensional nine-velocity (D2Q9) model, with equilibrium populations \cite{pooley-contact}:
 \begin{equation}
@@
 where $\Gamma$ is the mobility parameter; the chemical potential
-$\mu=-A\phi+A\phi^3-k\Delta\phi$; $k$ is the parameter related to the surface
-tension; $A$ is the parameter of the free-energy model. The bulk pressure
-is expressed as $p_0=c_s^2 \rho +A (-0.5 \phi^2+0.75 \phi^4)$ with
-the sound speed $c_s^2=1/3$. 
-Parameters specific to the D2Q9 grid are the weights
-$w_i=\left\{\frac{4}{9},\frac{1}{9},\frac{1}{9},\frac{1}{9},\frac{1}{9},
+$\mu=-A\phi+A\phi^3-k\Delta\phi$; $k$ is the parameter related to the surface tension; $A$ is the parameter of the free-energy model.
+The bulk pressure is expressed as $p_0=c_s^2 \rho +A (-0.5 \phi^2+0.75 \phi^4)$ with the sound speed $c_s^2=1/3$.
+Parameters specific to the D2Q9 grid are the weights $w_i=\left\{\frac{4}{9},\frac{1}{9},\frac{1}{9},\frac{1}{9},\frac{1}{9},
 \frac{1}{36},\frac{1}{36},\frac{1}{36},\frac{1}{36}\right\}$, and the tensor
 $Q_{i\alpha\beta}=c_{i\alpha} c_{i\beta} - c_s^2 \delta_{\alpha\beta}$.  
-Other weights 
-are as follows:
+Other weights are as follows:
 $w^{xx}_{1-2}=w^{yy}_{3-4}=1/3$, $w^{xx}_{3-4}=w^{yy}_{1-2}=-1/6$,
@@
 
-One can show that the set of discrete evolution equations (\ref{set:equilibrium:binary}) restores the
-macroscopic
+One can show that the set of discrete evolution equations (\ref{set:equilibrium:binary}) restores the macroscopic
 multiphase equations through the Chapman-Enskog analysis \cite{chapman}:
@@
 where $\nu=c_s^2 (\tau-1/2)$ is the viscosity,
-$M=\Gamma(\tau_{\phi}-1/2)$ is the mobility parameter, and $\tau=\frac{1}{\omega}$ and $\tau_{\phi}$
-are the relaxation parameters of density and phase fields, 
+$M=\Gamma(\tau_{\phi}-1/2)$ is the mobility parameter, and $\tau=\frac{1}{\omega}$ and $\tau_{\phi}$ are the relaxation parameters of density and phase fields, 
 $P_{\alpha\beta}=\Bigl(p_0-k\phi \Delta \phi -\frac{k}{2}|\nabla \phi|^2\Bigr)\delta_{\alpha\beta}
-+ k \partial_{\alpha} \phi \partial_{\beta} \phi$  \cite{pooley-contact}.The interface tension value
-in the framework of the binary liquid model is $\gamma=\sqrt{\frac{8 k
-A}{9}}$. The inclusion of the interface tension in the momentum flux tensor is done through the
-coefficients $k$, $A$ and weights $w_i^{\alpha\beta}$.
++ k \partial_{\alpha} \phi \partial_{\beta} \phi$  \cite{pooley-contact}.The interface tension value in the framework of the binary liquid model is $\gamma=\sqrt{\frac{8 k
+A}{9}}$. The inclusion of the interface tension in the momentum flux tensor is done through the coefficients $k$, $A$ and weights $w_i^{\alpha\beta}$.
 
@@
 the Navier-Stokes equations, i.e. the first two equations in (\ref{binary:fluid:system}). The second
-equation
-of system \ref{standard:implementation} simulates the phase governing equation, i.e. the third
-equation in
-(\ref{binary:fluid:system}). The system (\ref{binary:fluid:system}) allows the separation of the
-liquid
-phase with $\phi=1$ and a so-called gas phase with $\phi=-1$. The
-relaxation time is taken as linearly dependent on the relaxation
-times $\tau_{\mathrm{gas}}$ and $\tau_{\mathrm{liq}}$:
+equation of system \ref{standard:implementation} simulates the phase governing equation, i.e. the third
+equation in (\ref{binary:fluid:system}). The system (\ref{binary:fluid:system}) allows the separation of the
+liquid phase with $\phi=1$ and a so-called gas phase with $\phi=-1$. The relaxation time is taken as linearly dependent on the relaxation times $\tau_{\mathrm{gas}}$ and $\tau_{\mathrm{liq}}$:
 $\tau=\tau_{\mathrm{gas}}+\frac{\phi+1}{2}(\tau_{\mathrm{liq}}-\tau_{\mathrm{gas}})$. This allows
-to change viscosity from the gas viscosity
-$\nu_{\mathrm{gas}}=\frac{1}{3}\Bigl(\tau_{\mathrm{gas}}-\frac{1}{2}\Bigr)$ to the liquid viscosity
+to change viscosity from the gas viscosity $\nu_{\mathrm{gas}}=\frac{1}{3}\Bigl(\tau_{\mathrm{gas}}-\frac{1}{2}\Bigr)$ to the liquid viscosity
 $\nu_{\mathrm{liq}}=\frac{1}{3}\Bigl(\tau_{\mathrm{liq}}-\frac{1}{2}\Bigr)$ while phase changes
@@
 
-Note that the parameters of the lattice
-Boltzmann model, as the surface tension, viscosity, etc are connected with the physical parameters only through the non-dimensional
-numbers governing the physics of the problem.  Therefore, the parameters in the lattice Boltzmann system have certain degree of freedom and not proportional to the physical parameters.
+Note that the parameters of the lattice Boltzmann model, as the surface tension, viscosity, etc are connected with the physical parameters only through the non-dimensional numbers governing the physics of the problem.
+Therefore, the parameters in the lattice Boltzmann system have certain degree of freedom and not proportional to the physical parameters.
 
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{Figures/free_surface.eps}
+\begin{figure}[h!]
+\includegraphics[width=0.5\textwidth]{Figures/free_surface.eps}
 \caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \includegraphics[width=0.5\textwidth]{Figures/droplet_shapes_curved_substrates.eps}
@@
 
+\pagebreak
 \section{Results}
 
+Figure reference \ref{fig:droplet:shapes:curved:substrate:F1} \ref{fig:droplet:shapes:curved:substrate:F5} \ref{fig:extra:pressure}
+
+\begin{figure}[h!]
+\includegraphics[width=1\textwidth]{Figures/shapes_F1_Grad-20.eps}
+\caption{Droplet shape at simulation time step before succesful wetting for flow conditions characterized by body force paramerer F1 and contact angle conditions characterized by gradient parameter -20.
+A range of different initial droplet radius is shown (R=10,20,30,40,50) while the subtrate radius was kept constant (R=20)  \label{fig:droplet:shapes:curved:substrate:F1}}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=1\textwidth]{Figures/shapes_F5_Grad-20.eps}
+\caption{Droplet shape at simulation time step before succesful wetting for flow conditions characterized by body force paramerer F5 and contact angle conditions characterized by gradient parameter -20.
+A range of different initial droplet radius is shown (R=10,20,30,40,50) while the subtrate radius was kept constant (R=20)  \label{fig:droplet:shapes:curved:substrate:F5}}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=1\textwidth]{Figures/comparison_another_approach.eps}
+\caption{Extra pressure inside emulsion droplets measured at the timestep just before weeting the substrate for flow conditions characterized by body force parameter F1 full circles and F5 triagles.
+The solid line indicates the theoretical value for the laplace pressure for the different emulsion sizes.\label{fig:extra:pressure}}
+\end{figure}
+
+\pagebreak
 \section{Deposition efficiency map}
 
+Figure reference \ref{fig:deposition:map}
+
+\begin{figure}[h!]
+\includegraphics[width=1\textwidth]{Figures/results_map.eps}
+\caption{Deposition map.
+Label 1 stays for 1 droplet attached front, 2 stays for 1 droplet attached back, 3 stays for 2 droplets attached back, 4 stays for not attached, 5 stays for breakup to 2 droplets, 6 stays for breakup with coalescense\label{fig:deposition:map}}
+\end{figure}
+
+\pagebreak
 \section{Conclusions}
@@
 However a detailed analysis of the collision process reveals that droplets deformation at wetting critically depends on the collision speed and relative dimension of droplet and substrate.
-Large droplets approaching the substrate very slowly deform very mildly before wetting while during fast collision a higher deformation is achieved before wetting occurs.
+Large droplets approaching the substrate slowly deform very mildly before wetting while during fast collision a higher deformation is achieved before wetting occurs.
 For small droplets the same trend is found but overall smaller deformation are observed.
